\documentclass{memoir}
\title{Kristof's Birthday Thoughts - June 2018}
\author{Friends, Brothers and Sisters}
\renewcommand{\maketitlehookb}{\centering Thoughts, wishes, quotes and general beautiful thoughts to get lost in. \\ A journey into the unknown}
\begin{document}
\maketitle
\clearpage

\chapterprecishere{``I hope we can walk our path.''
\\  \\
\\
\textup{Yours forever.}
\par\raggedleft--- \textup{Isabelle} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Count your age by experiences and friends, not years.  Count your life by memorable moments and smiles, not tears.''
\\ (John Lennon) \\
\\
\textup{Together with my gratitude for the moments and experiences we have spent together ... and hopefully years more of them to come.}
\par\raggedleft--- \textup{Owen Kemp} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Who looks outside, dreams; who looks inside, awakes.''
\\ (Carl Jung) \\
\\
\textup{Thank you so much for making me look inside. May we be side by side in many ventures to make the world a better place.}
 \par\raggedleft--- \textup{Andreas Hartl} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Change is the only constant in life.''
\\ (Heraclitus) \\
\\
\textup{Let's create flow, a flow of change in this world where many things are in flux already -- Thank you sooo much for making me see.}
 \par\raggedleft--- \textup{Weynand Kuijpers} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Let the beauty of what you love be what you do.''
 \par\raggedleft--- \textup{Didem Gordon} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Be impeccable with your word. \\ Don't take anything personally. \\Don't make assumptions. \\ Always do your best''
\\ (Don Miguel Ruiz)
 \par\raggedleft--- \textup{Stela Suils Cuesta} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``The greatest leader is not necessarily the one who does the greatest things. He is the one that gets the people to do the greatest things.''
\\ (Ronald Reagan) \\
\\
\textup{Kristof, thank you for pushing us to be the best we can be, and to achieve greatness.}
 \par\raggedleft--- \textup{Sabrina Sadik} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``People can feel real Ikigai only when they proceed toward self-realization, in love and happiness, in their encounters with others, and through a sense of the value of life.''
\\ (Kobayashi Tsukasa)  \\
\\
\textup{Dear Kristof, I came across the beautiful concept of Ikagi recently. When expressed in this, its simplest form, \textit{``Ikigai is the process of allowing the self's possibilities to blossom,''} I thought, perhaps,  you might like it as much as I did.}
 \par\raggedleft--- \textup{Dan Leighton} }

\bigskip
\bigskip
\bigskip

 \chapterprecishere{``The Web as I envisaged it, we have not seen it yet. The future is still so much bigger than the past.''
 \\ (Tim Berners-Lee) \\

  ``I alone cannot change the world, but I can cast a stone across the water to create many ripples.''
 \\ (Mother Theresa) \\
 \\
 \textup{Dear Kristof, seems befitting to quote the founder of the internet and the most iconic evangelist of love
as a tribute to our leader and my friend :)
\\
\\Thank you for who you are, and what you do for all of us...}
 \par\raggedleft--- \textup{Chris Hutton} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Whatever happens in the future, trust in destiny''
\\
\\
 \textup{Kristof, tx for our past, looking forward to that destiny}
  \par\raggedleft--- \textup{Peter van der Henst} }

  \bigskip
  \bigskip
  \bigskip

\chapterprecishere{``And those who were seen dancing were thought to be insane by those who could not hear the music.''
\\ (Friedrich Nietzsche) \\
\par\raggedleft--- \textup{Reem Khramis} }

  \bigskip
  \bigskip
  \bigskip

\newpage
\chapterprecishere{Dare to Be \\
\\
When a new day begins, dare to smile gratefully.\\
When there is darkness, dare to be the first to shine a light.\\
When there is injustice, dare to be the first to condemn it.\\
When something seems difficult, dare to do it anyway.\\
When life seems to beat you down, dare to fight back.\\
When there seems to be no hope, dare to find some.\\
When you are feeling tired, dare to keep going.\\
When times are tough, dare to be tougher.\\
When love hurts you, dare to love again.\\
When someone is hurting, dare to help them heal.\\
When another is lost, dare to help them find the way.\\
When a friend falls, dare to be the first to extend a hand.\\
When you cross paths with another, dare to make them smile.\\
When you feel great, dare to help someone else feel great too.\\
When the day has ended, dare to feel as you have done your best.\\
Dare to be the best you can –--\\
At all times, Dare to be!
\\ (Steve Maraboli, Life, the Truth, and Being Free) \\
\par\raggedleft--- \textup{Georges Georgiou} }

  \bigskip
  \bigskip
  \bigskip

\chapterprecishere{``When we love, we always strive to become better than we are. When we strive to become better than we are, everything around us becomes better too.''
\\ (Paulo Coelho, The Alchemist) \\
\\
\textup{Let this quote from The Alchemist always be a reminder to us all that the strongest power we hold inside us is ``love'', it's what makes human, it's what makes us whole. And together with our combined love we can accomplish anything.}
\par\raggedleft--- \textup{Adnan Fatayerji} }

  \bigskip
  \bigskip
  \bigskip

\chapterprecishere{``Any intelligent fool can make things bigger and more complex… It takes a touch of genius – and a lot of courage to move in the opposite direction.''
\\ (Albert Einstein) \\
\\
 \textup{Thank you for the years of inspiration that have passed, and for the many more to come.}
\par\raggedleft--- \textup{Christophe De Carvalho Pereira Martins} }

\bigskip
\bigskip
\bigskip



\chapterprecishere{``Real quality means making sure that people are proud of the code they write, that they're involved and taking it personally.''
\\ (Linus Torvalds) \\
\\
 \textup{Thank you allowing me (and us) to write code of which I'm proud, for good causes and a better future.}
\par\raggedleft--- \textup{Maxime} }

\bigskip
\bigskip
\bigskip


\chapterprecishere{I believe that we are here to create Heaven on Earth. I do believe that every seed planted with love can grow into a flower, that every blossom can turn into a bloom under the warmth of a loving touch. I do believe that miracles do indeed happen when the intention is love. I believe that people like you, Kristof, are the ones who can, and do, change the world, making it a better place for all living beings. Thank you for being a creator, for making a difference, for including me in your journey.
\\  \\
 \textup{May Divine Love surround you and Be You -- always.
 \\With infinite love and gratitude.}
\par\raggedleft--- \textup{Daniela Nikolova} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{My soul honors your soul.  I honor the place in you where the entire Universe resides.  I honor the light, love, truth, beauty and peace within you, because it is also within me.  In sharing these things we are united, we are the same, we are one.
\\  \\
 \textup{Thank you you for the opportunity to grow alongside you and so many beautiful people. With gratitude, happy birthday! Namaste.}
\par\raggedleft--- \textup{Elena Anfimova} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Only dead fish go with the flow ''
\par\raggedleft--- \textup{Manu} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{There is no difficulty that enough love will not conquer,\\
no disease that enough love will not heal,\\
no door that enough love will not open, \\
no gulf that enough love will not bridge,\\
no wall that enough love will not throw down,\\
no sin that enough love will not redeem.\\
It makes no difference how deeply seated may be the trouble, how great the mistake. Sufficient realization of love will resolve it all.
\par\raggedleft--- \textup{Ragheb Abushahba} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{Believe you can change the world. \\
Work quickly, keep the tools unlocked, work whenever. \\
Know when to work alone and when to work together. \\
Share -- tools, ideas.  Trust your colleagues. \\
No politics. No Bureaucracy. [These are ridiculous in a garage.] \\
The customer defines a job well done. \\
Radical ideas are not bad ideas. \\
Invent different ways of working. \\
Make a contribution every day.  If it does not contribute, it does not leave the garage. \\
Believe that together we can do everything. \\
Invent.
\par\raggedleft--- \textup{Wolfgang Wittmer} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{MIND: I'm worried. \\
HEART: Just relax. \\
MIND: But, I'm totally lost now. \\
HEART: Just follow me. \\
MIND: But you've never been there before.\\
HEART: Trust me, you'll love it. \\
SOUL: If you two would shut up, I'd show you the map.
\\  \\
 \textup{Kristof, may you always be guided by your soul purpose. Through our intentions and action we will manifest the change we need in our reality together. All we need is love!}
\par\raggedleft--- \textup{Olivia Jurado} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Dank u Kristof voor meer dan een decennia vol met uitdagingen, inspiratie en positieve sfeer!''
\par\raggedleft--- \textup{Jo} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Fail early \\
Fail often, \\
But always fail forward.''
\\ (John C. Maxwell) \\
\\
 \textup{Thank you for teaching me how to fail forward, to learn from it, make adjustments and move on!}
\par\raggedleft--- \textup{Roel van Sabben} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Your time is limited, so don't waste it living someone else's life!''
\\ (Steve Jobs) \\
\\
 \textup{Dear Kristof, having worked with you for more than two decades, I very much started to appreciate your view on time and life. I hope not to lose you in the next two decades to come.}
\par\raggedleft--- \textup{ Sacha Vekeman} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``It's not what you look at that matters, it's what you see.
As far as I'm concerned, I see People, I see passion, I feel complicity.
You made us gather around this greater goal, and we are all assembled to make that happen. I'm having fun again.\\
\\
I know this: we're going to be old friends till we're old and senile, and then, we'll be new friends every day again ;-)
Did I tell you I love you? There! I said it.''
\par\raggedleft--- \textup{Jan De Landtsheer} }

\bigskip
\bigskip
\bigskip

\chapterprecishere{``Change will not come if we wait for some other person or some other time. We are the ones we've been waiting for. We are the change that we seek.''
\\ (Barack Obama) \\
\\
\textup{May you always be the change and the motivator to others for a better world.}
\par\raggedleft--- \textup{Nayer Sobhy} }

\bigskip
\bigskip
\bigskip


\end{document}
