\documentclass{memoir}

\begin{document}


\chapterprecishere{``Count your age by experiences and friends, not years.  Count your life by memorable moments and smiles, not tears.''
\\ (John Lennon) \\
\\
\textup{Together with my gratitude for the moments and experiences we have spent together ... and hopefully years more of them to come.}
\par\raggedleft--- \textup{Owen Kemp} }

\bigskip
\bigskip

\chapterprecishere{``Who looks outside, dreams; who looks inside, awakes.'' 
\\ (Carl Jung) \\
\\
\textup{Thank you so much for making me look inside. May we be side by side in many ventures to make the world a better place.}
 \par\raggedleft--- \textup{Andreas Hartl} }

\bigskip
\bigskip

\chapterprecishere{``Change is the only constant in life.'' 
\\ (Heraclitus) \\
\\
\textup{Let's create flow, a flow of change in this world where many things are in flux already --- Thank you soo much for making me see.}
 \par\raggedleft--- \textup{Weynand Kuijpers} }

\bigskip
\bigskip

\chapterprecishere{``Let the beauty of what you love be what you do.'' 
\\
 \par\raggedleft--- \textup{Didem Gordon} }

\bigskip
\bigskip

\chapterprecishere{``Be impeccable with your words. \\ Don't take anything personally. \\Don't make assumptions. \\ Always do your best'' 
\\ (Don Miguel Ruiz) \\
\\
 \par\raggedleft--- \textup{Stela Suils Cuesta} }
 
\bigskip
\bigskip

\chapterprecishere{``The greatest leader is not necessarily the one who does the greatest things. He is the one that gets the people to do the greatest things.'' 
\\ (Ronald Reagan) \\
\\
\textup{Kristof, thank you for pushing us to be the best we can be, and to achieve greatness.}
 \par\raggedleft--- \textup{Sabrina Sadik} }

\bigskip
\bigskip

\chapterprecishere{``People can feel real Ikigai only when they proceed toward self-realization, in love and happiness, in their encounters with others, and through a sense of the value of life.'' 
\\ (Kobayashi Tsukasa)  \\
\\
\textup{Ikigai - the process of allowing the self's possibilities to blossom}
 \par\raggedleft--- \textup{Dan Leighton} }
 
\bigskip
\bigskip
 
 \chapterprecishere{``The Web as I envisaged it, we have not seen it yet. The future is still so much bigger than the past.''
 \\ (Time Berners Lee) \\

 \bigskip

  ``I alone cannot change the world, but I can cast a stone across the water to create many ripples.''
 \\ (Mother Theresa) \\
 \\
 \textup{Dear Kristof, seems befitting to quote the founder of the internet and the most iconic evangelist of love
as a tribute to our leader and my friend :). Thank you for who you are and what you do for all of us...}
 \par\raggedleft--- \textup{Chris Hutton} }

\bigskip
\bigskip

\chapterprecishere{``Whatever happens in the future, trust in destiny''
\\  \\
\\
 \textup{Kristof, tx for the past, looking forward to the destiny}
  \par\raggedleft--- \textup{Peter van der Henst} }
 
\end{document}
